---
title: "select_tone_paper"
author: "Ola Ozernov-Palchik"
date: "11/1/2020"
output:
  html_document:
    df_print: paged
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Adult Analysis

## Load packages and organize data 

```{r, include=FALSE, echo=FALSE}
Packages <- c("dplyr", "readr", "magrittr", "tidyr", "ggplot2", "lme4", "lmerTest",
              "emmeans", "sjstats","dabestr","gridExtra",'knitr','psych',
              'lmPerm',"lavaan",'MASS','tidyverse','psych','mice',"rstatix")
lapply(Packages, library, character.only = TRUE)
source('making_path_diagrams.R') #import the path-making-function

#dir<-dirname(rstudioapi::getActiveDocumentContext()$path)
#setwd("dir")
setwd("~/Dropbox (MIT)/GitHub/speech_specific_deficit_paper")
d=read.csv("data/abcd_beh_122020.csv")

groups=read.csv("data/abcd_group.csv")
snr=read.csv("data/SNR.csv")
music=read.csv("data/ABCD_music_data.csv")
tone=read.csv("data/tone_jnd_ntd_062721.csv")
sa=read.csv("data/dys_comp_selec_adapt_122020.csv")
tone_sa=merge(tone,sa)
#accuracy<-read.csv("sa_accuracy.csv")

music$music_y_n<-ifelse(music$music_y_n == 'Yes',1,0) 
music$music_y_n<-as.factor(music$music_y_n)

names(music)[names(music)=="ABCD.ID"] <- "PartID"
names(groups)[names(groups)=="ID"] <- "PartID"
names(d)[names(d)=="abcd_id"] <- "PartID"
d$PA<-(rowMeans(d[c('ctopp_elision_ss_2','ctopp_blending_ss_2')], na.rm=TRUE))
#d$WID<-(rowMeans(d[c('wrmt_id_ss','wrmt_wa_ss','towre_pde_ss','towre_sw_ss')], na.rm=TRUE))

d=merge(d,groups,
        by='PartID',all=TRUE)
d=merge(d,tone_sa,'PartID',all=TRUE)
#d=merge(d,accuracy,'PartID',all=TRUE)

d=merge(d,snr,'PartID',all=FALSE)

#names(d)[names(d)=="m_jnd"] <- "tone_thresh"
names(d)[names(d)=="slope"] <- "m_slope"
names(d)[names(d)=="d"] <- "select_sloped"
names(d)[names(d)=="adapt"] <- "adaptor_diff"
#names(d)[names(d)=="m_fd_hz"] <- "ntd"

d_m=merge(d,music,'PartID',all=TRUE)

```

```{r}
hist(d$adaptor_diff)
```

## Group beh differences
```{r, echo=FALSE}
# table(d$Subgroup,d$sex.x)
# beh_a<-d%>%ungroup%>%dplyr::select(Subgroup.x,background_age,kbit_ss_2,wrmt_id_ss_2,wrmt_wa_ss_2,towre_sw_ss_2,towre_pde_ss_2,ppvt_vocab_ss_2,gort_ori_ss_2,ctopp_blending_ss_2,ctopp_elision_ss_2,ctopp_nonword_ss_2,ran_2set_ss_2)
# 
# library(arsenal)
# table_one <- tableby(Subgroup ~ ., data = beh_a)
# summary(table_one, title = "Behavioral Data Adults")
# beh_a %>% cohens_d(ctopp_nonword_ss_2~ Subgroup, var.equal = TRUE)
# chisq.test(d2$Subgroup,d2$background_sex)

```


# Music Analysis
```{r, echo=FALSE,include=FALSE}

hist(d_m$total_years)
table(d_m$music_y_n)
d_m2<-d_m %>%
  dplyr::filter(music_y_n=='1')
sd(d_m$total_years)
d_group<-d_m%>%dplyr::filter(Subgroup.x=="DD"|Subgroup.x=="TYP")
range(d_m$total_years)
t.test(d_group$tot_music~d_group$Subgroup.x)
tbl = table(d_group$music_y_n,d_group$Subgroup.x)
tbl
chisq.test(tbl)
anova(lm(tone_thresh~music_y_n+Subgroup.x, data=d_group)) #group differences sig after PA and SNR partialed out
anova(lm(m_slope~music_y_n+Subgroup.x, data=d_group)) #group differences sig after PA and SNR partialed out
#anova(lm(diff_8~music_y_n+Subgroup.x, data=d_group)) #group differences sig after PA and SNR partialed out
anova(lm(ntd~music_y_n+Subgroup.x, data=d_group)) #group differences sig after PA and SNR partialed out
summary(lm(ctopp_blending_ss~select_sloped,data=d))

```
### SIN Analysis 
```{r,echo=FALSE}
t.test(d_m$quicksin_snr_loss_2~d_m$Subgroup.x)

```

### Adult: Correlations
```{r,echo=FALSE}


d_a3<-d%>%filter(age=='Adult')%>% dplyr::select(tone_thresh,ntd,m_slope,adaptor_diff,PA)

resa <- cor(na.omit(d_a3,method = "fisher"))
#d_a3<-na.omit(d_a3)%>%filter(adaptor_diff!='Inf'& adaptor_diff>-4.7)
length(d_a3$ntd)
#create a table with r and p
source("corstars_function.R")
corstars(d_a3,method="spearman")#you need to run the function first
p.adjust(0.01, method = "holm", n = length(resa))

#test for strengh of correlation
paired.r(-.40,.06,NULL,50) #independent correlations same sample size



```



###Adult: Correlations by group-TYP
```{r,echo=FALSE}
dd<-d%>%filter(age=='Adult')%>%dplyr::filter(Subgroup=='DD')
dd<-na.omit(dd%>%ungroup() %>% dplyr::select(tone_thresh,ntd,m_slope,adaptor_diff,PA))


typ<-d%>%filter(age=='Adult')%>%filter(Subgroup=='TYP')
typ<-na.omit(typ%>%ungroup() %>% dplyr::select(tone_thresh,ntd,m_slope,adaptor_diff,PA))
corstars(typ,method="spearman")#you need to run the function first

#correlation between ntd and adapt_diff
typ2<-d_m%>%filter(age=='Adult')%>%filter(Subgroup.x=='TYP')
summary(lm(ntd~background_age+background_sex+tone_thresh+ctopp_nonword_ss+quicksin_snr_loss+m_slope+adaptor_diff,data=typ2))

m3<-lm(PA~tone_thresh+ctopp_nonword_ss+quicksin_snr_loss+ntd+adaptor_diff+quicksin_snr_loss,data=typ2)
summary(m3)

t2<-lm(adaptor_diff~m_slope+ctopp_nonword_ss,data=typ2)
typ2$adap_res<-resid(t2)

m3<-lm(ntd~tone_thresh+ctopp_nonword_ss+quicksin_snr_loss+adap_res,data=typ2)
summary(m3)
summary(m3)$r.squared
effectsize::standardize_parameters(m3)
t1<-lm(ntd~tone_thresh+ctopp_nonword_ss+quicksin_snr_loss,data=typ2)
t2<-lm(adaptor_diff~m_slope+ctopp_nonword_ss+quicksin_snr_loss,data=typ2)

typ2$ntd_res<-resid(t1)
typ2$adap_res<-resid(t2)
cor.test(typ2$ntd_res,typ2$adap_res)
plot(typ2$ntd_res,typ2$adap_res)


```

###Adult: Correlations by group-DYS
```{r,echo=FALSE}
#correlation between ntd and adapt_diff
dd2<-d_m%>%filter(age=='Adult')%>%filter(Subgroup.x=='DD')
summary(lm(ntd~background_age+background_sex+tone_thresh+ctopp_nonword_ss+quicksin_snr_loss+m_slope+adaptor_diff,data=dd2))
d1<-lm(ntd~tone_thresh+ctopp_nonword_ss+quicksin_snr_loss,data=dd2)
d2<-lm(adaptor_diff~m_slope+ctopp_nonword_ss+quicksin_snr_loss,data=dd2)

dd2$ntd_res<-resid(d1)
dd2$adap_res<-resid(d2)
cor.test(dd2$ntd_res,dd2$ctopp_nonword_ss)

#correlationa table
corstars(dd,method="spearman")#you need to run the function first
plot(dd$adaptor_diff,dd$PA) #check for outliers...
```


### Adult: Mediation Analysis
```{r,echo=FALSE}
#check assumptions

d_a3 %>% ungroup %>% 
  dplyr::select(tone_thresh, m_slope, PA,adaptor_diff) %>% 
  pairs.panels()


#check variance
varTable(d_a3)

#d2$m_slope<-log10(d3$m_slope)

#http://lavaan.ugent.be/tutorial/mediation.html
#https://nmmichalak.github.io/nicholas_michalak/blog_entries/2018/nrg01/nrg01.html
```

#### Model 1 JND
```{r,echo=FALSE}

da1<-d_a3%>%ungroup %>% dplyr::select(m_slope,tone_thresh, PA)

model_h1<-'#direct effect
  PA~c*tone_thresh
#mediator
  m_slope~a*tone_thresh
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'

#run mediation analysis with bootstrapping
fit_h1<-lavaan::sem(model_h1, data=d_a3,bootstrap=10000)
summary(fit_h1,fit.measures=T, rsq=T)

#created bootsrapped confidence intervals
boot.fit_h1<-lavaan::parameterEstimates(fit_h1, boot.ci.type = "bca.simple",level = 0.95, 
                             ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_h1 #model

###create path diagram

med_data1 <-
  data.frame(
    lab_x   = "Tone\\ndiscrimination",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawareness",
    coef_xm = toAnnot(boot.fit_h1,2),#toString(round(boot.fit_h1$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_h1,3),#toString(round(boot.fit_h1$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_h1,1),' (',toAnnot(boot.fit_h1,7),')',sep='')
  )
med_diagram(med_data1)

```

#### Model 2 NTD
```{r,echo=FALSE}
da2<-d_a3%>%ungroup %>% dplyr::select(m_slope,ntd, PA)
m2<-psych::mediate(PA ~ ntd + (m_slope), data=da2)

model_h2<-'#direct effect
  PA~c*ntd
#mediator
  m_slope~a*ntd
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'

#run mediation analysis with bootstrapping
fit_h2<-lavaan::sem(model_h2, data=da2,bootstrap=10000)
summary(fit_h2,fit.measures=T, rsq=T)
boot.fit_h2<-lavaan::parameterEstimates(fit_h2, boot.ci.type = "bca.simple",level = 0.95,
                                        ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_h2


med_data2 <-
  data.frame(
    lab_x   = "Tone\\nanchoring",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawareness",
    coef_xm = toAnnot(boot.fit_h2,2),#toString(round(boot.fit_h2$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_h2,3),#toString(round(boot.fit_h2$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_h2,1),' (',toAnnot(boot.fit_h2,7),')',sep='')
  )
med_diagram(med_data2)

```

#### Model 3 Adaptation

```{r,echo=FALSE}
### H3: Y=PA, X=adaptor_diff, M=select_adapt
da3<-d_a3%>%ungroup %>% dplyr::select(m_slope,adaptor_diff, PA)

model_h3<-'#direct effect
  PA~c*adaptor_diff
#mediator
  m_slope~a*adaptor_diff
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'
#run mediation analysis with bootstrapping
fit_h3<-lavaan::sem(model_h3, data=da3,bootstrap=10000)
summary(fit_h3,fit.measures=T, rsq=T)
boot.fit_h3<-lavaan::parameterEstimates(fit_h3, boot.ci.type = "bca.simple",level = 0.95, 
                                      ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_h3

med_data3 <-
  data.frame(
    lab_x   = "Speech\\nadaptation",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawareness",
    coef_xm = toAnnot(boot.fit_h3,2),#toString(round(boot.fit_h2$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_h3,3),#toString(round(boot.fit_h2$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_h3,1),' (',toAnnot(boot.fit_h3,7),')',sep='')
  )
med_diagram(med_data3)
```

## Adult Dyslexia Only

#### Adult Dys: Model 1 JND
```{r,echo=FALSE}
dd<-d%>%filter(age=='Adult')%>%dplyr::filter(Subgroup=='DD') %>% dplyr::select(m_slope,tone_thresh, PA)

###H1: #Y=PA, X=tone threshold, M=slectAdapt slope

model_h4<-'#direct effect
  PA~c*tone_thresh
#mediator
  m_slope~a*tone_thresh
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'

#run mediation analysis with bootstrapping
fit_h4<-lavaan::sem(model_h4, data=dd,bootstrap=10000)
summary(fit_h4,fit.measures=T, rsq=T)

#created bootsrapped confidence intervals
boot.fit_h4<-lavaan::parameterEstimates(fit_h4, boot.ci.type = "bca.simple",level = 0.95, 
                                        ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_h4


med_data4 <-
  data.frame(
    lab_x   = "Tone\\ndiscrimination",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawareness",
    coef_xm = toAnnot(boot.fit_h4,2),#toString(round(boot.fit_h2$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_h4,3),#toString(round(boot.fit_h2$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_h4,1),' (',toAnnot(boot.fit_h4,7),')',sep='')
  )
med_diagram(med_data4)
```
#### Adult Dys: Model 2 NTD
```{r,echo=FALSE}
### H2: Y=PA, X=ntd, M=select_adapt
dd<-d%>%filter(age=='Adult')%>%dplyr::filter(Subgroup=='DD') %>% dplyr::select(m_slope,ntd, PA)

model_h5<-'#direct effect
  PA~c*ntd
#mediator
  m_slope~a*ntd
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'

#run mediation analysis with bootstrapping
fit_h5<-lavaan::sem(model_h5, data=dd,bootstrap=10000)
summary(fit_h5,fit.measures=T, rsq=T)
boot.fit_h5<-lavaan::parameterEstimates(fit_h5, boot.ci.type = "bca.simple",level = 0.95,
                                        ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_h5


med_data5 <-
  data.frame(
    lab_x   = "Tone\\nanchoring",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawareness",
    coef_xm = toAnnot(boot.fit_h5,2),#toString(round(boot.fit_h2$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_h5,3),#toString(round(boot.fit_h2$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_h5,1),' (',toAnnot(boot.fit_h5,7),')',sep='')
  )
med_diagram(med_data5)
```
#### Adult Dys: Model 3 Adaptation

```{r,echo=FALSE}
dd<-d%>%filter(age=='Adult')%>%dplyr::filter(Subgroup=='DD') %>% dplyr::select(m_slope,adaptor_diff, PA)

### H3: Y=PA, X=adaptor_diff, M=select_adapt

model_h6<-'#direct effect
  PA~c*adaptor_diff
#mediator
  m_slope~a*adaptor_diff
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'
#run mediation analysis with bootstrapping
fit_h6<-lavaan::sem(model_h6, data=dd,bootstrap=10000)
summary(fit_h6,fit.measures=T, rsq=T)
boot.fit_h6<-lavaan::parameterEstimates(fit_h6, boot.ci.type = "bca.simple",level = 0.95, 
                                        ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_h6

med_data6 <-
  data.frame(
    lab_x   = "Speech\\nadaptation",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawarness",
    coef_xm = toAnnot(boot.fit_h6,2),#toString(round(boot.fit_h2$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_h6,3),#toString(round(boot.fit_h2$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_h6,1),' (',toAnnot(boot.fit_h6,7),')',sep='')
  )
med_diagram(med_data6)
```

# Child Analysis

## Child: Organize Data
```{r, echo=FALSE, include=FALSE}
d_c<-tone_sa%>%filter(age=="Child")
#d_c<-read.csv("data/dys_comp_selec_adapt_122020.csv")
#d_c2<-d_c%>%filter(age=='Child')
Missing_patterns <-md.pattern(d_c)
beh_c<-read.csv("data/child_data.csv")
d_c$PartID[!(d_c$PartID %in% beh_c$PartID)] #READ_6103"
beh_c$PartID[!(beh_c$PartID %in% d_c$PartID)] 
beh2<-read.csv("data/all_beh.csv")
names(beh2)[names(beh2)=="ID"] <- "PartID" 

set.seed(182)
init = mice(beh_c, maxit=0)
meth = init$method
predM = init$predictorMatrix
predM[, c("PartID")]=0
imputed = mice(beh_c, method=meth, predictorMatrix=predM, m=50)
imputed <- complete(imputed)
#apply(imputed,2,pMiss)
beh_c2<-imputed
str(beh_c2)
Missing_patterns <-md.pattern(beh_c2)
Missing_patterns

d_c2<-merge(d_c,beh_c2,"PartID")
d_c2<-merge(x = d_c2, y = beh2[ , c("PartID", "NonWord")], by = "PartID", all.x=TRUE)




#names(d)[names(d)=="m_jnd"] <- "tone_thresh"
names(d_c2)[names(d_c2)=="slope"] <- "m_slope"
names(d_c2)[names(d_c2)=="d_c2"] <- "select_sloped"
names(d_c2)[names(d_c2)=="adapt"] <- "adaptor_diff"
#names(d)[names(d)=="m_fd_hz"] <- "ntd"

d_c2$PA<-(rowMeans(d_c2[c('ctel','ctbw')]))
#d_c$WID<-(rowMeans(d_c2[c('WID','WWA','twse','tpde')], na.rm=TRUE))
d_c2$adaptor_diff<-as.numeric(d_c2$adaptor_diff)
hist(d_c2$adaptor_diff)

# d_c2=d_c2%>% 
#   dplyr::group_by(PartID)%>% 
#   dplyr::summarize(m_slope = ((select_slopeb+select_sloped)/2))%>% #mean select adapt slope
#   left_join(d_c2, by = "PartID") 

```
## Behavioral comparisons
```{r, echo=FALSE}
table(d_c2$gender,d_c2$group.x) #1=male, 2=female
beh_c3<-d_c2%>%ungroup%>%dplyr::select(group.x,age.x,KBITss,WID,WWA,twse,tpde,ppvt,gort_roi,ctbw,ctel,ran_2)

library(arsenal)
table_one <- tableby(group ~ ., data = beh_c)
summary(table_one, title = "Behavioral Data Child")
names(beh_c3)
beh_c3 %>% rstatix::cohens_d(KBITss~ group.x, var.equal = TRUE)
```

## Child Correlations
```{r,echo=FALSE}
d_c3<-d_c2%>%ungroup() %>% dplyr::select(tone_thresh,ntd,m_slope,adaptor_diff,PA)
d_c3<-na.omit(d_c3)

#you need to run the function first
source("corstars_function.R")
corstars(d_c3, method="spearman")
```

###Child Correlation by Group

#### Child Dys

```{r,echo=FALSE}
### by DYS group ###

d_dd_c<-d_c2%>%filter(group.x=='Dys')
d_dd_c$PartID<-NULL

d_dd_c2<-d_dd_c%>%dplyr::select(tone_thresh,ntd,m_slope,adaptor_diff,PA)
str(d_dd_c2)
resa <- cor(na.omit(d_dd_c2,method = "pearson"))
d_dd_c<-na.omit(d_dd_c2)
#create a table with r and p
corstars(d_dd_c2,method="spearman")#you need to run the function first

```

###Test correlation magnitude
```{r, echo=FALSE}
library(cocor)
#Slope and JND (dys child)
##tc
cocor.indep.groups(-.35, -.10, 20, 30, alternative = "less", test = "all", alpha = 0.05)

##da
cocor.indep.groups(-.35,-.15, 18, 21, alternative = "less", test = "all", alpha = 0.05)
##ta
cocor.indep.groups(0.08, -.34, 30,22, alternative = "greater", test = "all", alpha = 0.05)

#Slope and Adapt in Children, not adults
cocor.indep.groups(.38, .19, 48,45, alternative = "greater", test = "all", alpha = 0.05)

#JND and Slope in Children, not adults

```
#### Plot NTD and PA in Child
```{r,echo=FALSE}
#what does the PA and NTD correlation look like
ggplot(d_dd_c2, aes(x = ntd, y = PA)) +
  stat_smooth (
    method = "glm",
    formula = y ~ x,
    # colour = "black",
    size = 1
  ) +
  geom_point(aes (size = 5)) +
  scale_shape_manual(values = c(1, 17)) +
  labs(x = "NTD", y = "PA") +
  theme(
    axis.title = element_text(family = "Trebuchet MS", size = 20),
    legend.position ="none",
    legend.text = element_blank(),
    legend.title = element_blank(),
    panel.background = element_rect(fill = "transparent", colour = NA), 
    plot.background = element_rect(fill = "transparent", colour = NA),
    axis.line = element_line(colour = "black"),
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15))


#try without outlier
test<-d_dd_c2%>%filter(d_dd_c2$PA>6)
corstars(test,method="spearman")#you need to run the function first
```

#### Child Typ
```{r,echo=FALSE}
### by TYP group ###
d_t_c<-d_c2%>%filter(group.x=='Typ')
d_t_c<-d_t_c%>%ungroup() %>% dplyr::select(tone_thresh,ntd,m_slope,adaptor_diff,PA)
resct <- cor(na.omit(d_t_c,method = "spearman"))
d_t_c2<-na.omit(d_t_c)
#create a table with r and p
corstars(d_t_c2,method="spearman")#you need to run the function first
```

### Try Bayesian Correlation 
```{r,echo=FALSE}
library(BayesFactor)
library(bayestestR)

#All Adults
correlationBF(d_a3$tone_thresh, d_a3$ntd)
correlationBF(d_a3$tone_thresh, d_a3$m_slope)
correlationBF(d_a3$tone_thresh, d_a3$adaptor_diff)
correlationBF(d_a3$tone_thresh, d_a3$PA)

correlationBF(d_a3$ntd, d_a3$m_slope)
correlationBF(d_a3$ntd, d_a3$adaptor_diff)
correlationBF(d_a3$ntd, d_a3$PA)

correlationBF(d_a3$m_slope, d_a3$adaptor_diff)
correlationBF(d_a3$m_slope, d_a3$PA)

correlationBF(d_a3$adaptor_diff, d_a3$PA)


#All Children
correlationBF(d_c3$tone_thresh, d_c3$ntd)
correlationBF(d_c3$tone_thresh, d_c3$m_slope)
correlationBF(d_c3$tone_thresh, d_c3$adaptor_diff)
correlationBF(d_c3$tone_thresh, d_c3$PA)

correlationBF(d_c3$ntd, d_c3$m_slope)
correlationBF(d_c3$ntd, d_c3$adaptor_diff)
correlationBF(d_c3$ntd, d_c3$PA)

correlationBF(d_c3$m_slope, d_c3$adaptor_diff)
correlationBF(d_c3$m_slope, d_c3$PA)

correlationBF(d_c3$adaptor_diff, d_c3$PA)

#Typ Adults

correlationBF(typ$tone_thresh, typ$ntd)
correlationBF(typ$tone_thresh, typ$m_slope)
correlationBF(typ$tone_thresh, typ$adaptor_diff)
correlationBF(typ$tone_thresh, typ$PA)

correlationBF(typ$ntd, typ$m_slope)
correlationBF(typ$ntd, typ$adaptor_diff)
correlationBF(typ$ntd, typ$PA)

correlationBF(typ$m_slope, typ$adaptor_diff)
correlationBF(typ$m_slope, typ$PA)

correlationBF(typ$adaptor_diff, typ$PA)
#Dys Adults

correlationBF(typ$tone_thresh, typ$ntd)
correlationBF(typ$tone_thresh, typ$m_slope)
correlationBF(typ$tone_thresh, typ$adaptor_diff)
correlationBF(typ$tone_thresh, typ$PA)

correlationBF(typ$ntd, typ$m_slope)
correlationBF(typ$ntd, typ$adaptor_diff)
correlationBF(typ$ntd, typ$PA)

correlationBF(typ$m_slope, typ$adaptor_diff)
correlationBF(typ$m_slope, typ$PA)

correlationBF(typ$adaptor_diff, typ$PA)

#Typ Children

#Dys Children


```

## Child: Mediation Analysis
```{r,echo=FALSE}
#check assumptions
d_c4<-d_c2 %>% ungroup %>% 
  dplyr::select(tone_thresh, m_slope, PA,adaptor_diff,group.x) %>% 
  pairs.panels()
#d_c4<-d_c3%>%filter(tone_thresh<300) #remove an outlier
```

#### Child: Model 1 JND
```{r,echo=FALSE}

###H1: #Y=PA, X=tone threshold, M=slectAdapt slope
d_c_1=d_c2 %>% ungroup %>% 
  dplyr::select(tone_thresh, m_slope, PA)
d_c_1<-na.omit(d_c_1)

model_h1<-'#direct effect
  PA~c*tone_thresh
#mediator
  m_slope~a*tone_thresh
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'

#run mediation analysis with bootstrapping
fit_c_h1<-lavaan::sem(model_h1, data=d_c_1,bootstrap=10000)
summary(fit_c_h1,fit.measures=T, rsq=T)

#created bootsrapped confidence intervals
boot.fit_h1<-lavaan::parameterEstimates(fit_c_h1, boot.ci.type = "bca.simple",level = 0.95, 
                                     ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_h1


med_data1 <-
  data.frame(
    lab_x   = "Tone\\ndiscrimination",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawareness",
    coef_xm = toAnnot(boot.fit_h1,2),#toString(round(boot.fit_h1$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_h1,3),#toString(round(boot.fit_h1$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_h1,1),' (',toAnnot(boot.fit_h1,7),')',sep='')
  )
med_diagram(med_data1)

```
#### Child: Model 2 NTD
```{r,echo=FALSE}
### H2: Y=PA, X=ntd, M=select_adapt
d_c_2=d_c2 %>% ungroup %>% 
  dplyr::select(m_slope, ntd, PA)
d_c_2<-na.omit(d_c_2)

model_h2<-'#direct effect
  PA~c*ntd
#mediator
  m_slope~a*ntd
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'

#run mediation analysis with bootstrapping
fit_h2<-lavaan::sem(model_h2, data=d_c_2,bootstrap=1000)
summary(fit_h2,fit.measures=T, rsq=T)
boot.fit_h2<-lavaan::parameterEstimates(fit_h2, boot.ci.type = "bca.simple",level = 0.95,
                                     ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_h2

med_data2 <-
  data.frame(
    lab_x   = "Tone\\nanchoring",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawareness",
    coef_xm = toAnnot(boot.fit_h2,2),#toString(round(boot.fit_h2$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_h2,3),#toString(round(boot.fit_h2$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_h2,1),' (',toAnnot(boot.fit_h2,7),')',sep='')
  )
med_diagram(med_data2)
```
#### Child: Model 3 Adaptation
```{r,echo=FALSE}
###H3: #Y=PA, X=adaptor_diff, M=slectAdapt slope
d_c4=d_c2 %>% ungroup %>% 
  dplyr::select(adaptor_diff, m_slope, PA)
d_c4<-na.omit(d_c4)
model_c_h3<-'#direct effect
  PA~c*adaptor_diff
#mediator
  m_slope~a*adaptor_diff
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'

fit_c_h3<-lavaan::sem(model_c_h3, data=d_c4,bootstrap=1000)
summary(fit_c_h3,fit.measures=T, rsq=T)
boot.fit_c_h3<-lavaan::parameterEstimates(fit_c_h3, boot.ci.type = "bca.simple",level = 0.95, 
                                        ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_c_h3


med_data3 <-
  data.frame(
    lab_x   = "Speech\\nadaptation",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawareness",
    coef_xm = toAnnot(boot.fit_c_h3,2),#toString(round(boot.fit_c_h3$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_c_h3,3),#toString(round(boot.fit_c_h3$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_c_h3,1),' (',toAnnot(boot.fit_c_h3,7),')',sep='')
  )
med_diagram(med_data3)
```

## Child: Dyslexia only

#### Child DYS: Model 1 JND
```{r,echo=FALSE}
dd_c<-d_c2%>%filter(group.x=='Dys')
dd_c_1=dd_c %>% ungroup %>% 
  dplyr::select(tone_thresh, m_slope, PA)
dd_c_1<-na.omit(dd_c_1)

###H1: #Y=PA, X=tone threshold, M=slectAdapt slope

model_h1<-'#direct effect
  PA~c*tone_thresh
#mediator
  m_slope~a*tone_thresh
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'

#run mediation analysis with bootstrapping
fit_c_h1<-lavaan::sem(model_h1, data=dd_c_1,bootstrap=10000)
summary(fit_c_h1,fit.measures=T, rsq=T)

#created bootsrapped confidence intervals
boot.fit_h1<-lavaan::parameterEstimates(fit_c_h1, boot.ci.type = "bca.simple",level = 0.95, 
                                        ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_h1


med_data1 <-
  data.frame(
    lab_x   = "Tone\\ndiscrimination",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawareness",
    coef_xm = toAnnot(boot.fit_h1,2),#toString(round(boot.fit_h2$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_h1,3),#toString(round(boot.fit_h2$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_h1,1),' (',toAnnot(boot.fit_h1,7),')',sep='')
  )
med_diagram(med_data1)
```

#### Child DYS: Model 2 NTD
```{r,echo=FALSE}
### H2: Y=PA, X=ntd, M=m_slope
dd_c_2=dd_c %>% ungroup %>% 
  dplyr::select(ntd, m_slope, PA)
dd_c_2<-na.omit(dd_c_2)
model_h2<-'#direct effect
  PA~c*ntd
#mediator
  m_slope~a*ntd
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'

#run mediation analysis with bootstrapping
fit_h2<-lavaan::sem(model_h2, data=dd_c_2,bootstrap=10000)
summary(fit_h2,fit.measures=T, rsq=T)
boot.fit_h2<-lavaan::parameterEstimates(fit_h2, boot.ci.type = "bca.simple",level = 0.95,
                                        ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_h2

med_data2 <-
  data.frame(
    lab_x   = "Tone\\nanchoring",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawareness",
    coef_xm = toAnnot(boot.fit_h2,2),#toString(round(boot.fit_h2$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_h2,3),#toString(round(boot.fit_h2$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_h2,1),' (',toAnnot(boot.fit_h2,7),')',sep='')
  )
med_diagram(med_data2)
```

#### Child DYS: Model 3 Adaptation
```{r,echo=FALSE}

###H3: #Y=PA, X=adaptor_diff, M=slectAdapt slope

model_c_h3<-'#direct effect
  PA~c*adaptor_diff
#mediator
  m_slope~a*adaptor_diff
  PA~b*m_slope
# indirect effect (a*b)
  ab := a*b
# total effect
  total := c + (a*b)'

fit_c_h3<-lavaan::sem(model_c_h3, data=dd_c,bootstrap=1000)
summary(fit_c_h3,fit.measures=T, rsq=T)
boot.fit_c_h3<-lavaan::parameterEstimates(fit_c_h3, boot.ci.type = "bca.simple",level = 0.95, 
                                          ci=TRUE,pval=TRUE,standardized = FALSE)
boot.fit_c_h3


med_data3 <-
  data.frame(
    lab_x   = "Speech\\nadaptation",
    lab_m   = "Categorical\\nperception",
    lab_y   = "Phonological\\nawareness",
    coef_xm = toAnnot(boot.fit_h3,2),#toString(round(boot.fit_h2$est[2],digits = 2)),
    coef_my = toAnnot(boot.fit_h3,3),#toString(round(boot.fit_h2$est[3],digits = 2)),
    coef_xy = paste(toAnnot(boot.fit_h3,1),' (',toAnnot(boot.fit_h3,7),')',sep='')
  )
med_diagram(med_data3)
```

#### Demo ####

## Adult 
```{r}
# demo<-read.csv("abcd_demo.csv")
# d2 <- read.csv('data/abcd_beh_data_052421.csv',stringsAsFactors = FALSE,skipNul = TRUE,
#               blank.lines.skip = TRUE)
# names(d2)[names(d2)=="background_age"] <- "Age"
# names(d2)[names(d2)=="background_sex"] <- "Sex"
# names(d2)[names(d2)=="wrmt_wa_ss_2"] <- "WA"
# names(d2)[names(d2)=="ran_letters_ss_2"] <- "RAN_Letters"
# names(d2)[names(d2)=="wrmt_id_ss_2"] <- "WID"
# names(d2)[names(d2)=="towre_sw_ss_2"] <- "SWE"
# names(d2)[names(d2)=="towre_pde_ss_2"] <- "PDE"
# names(d2)[names(d2)=="ppvt_vocab_ss_2"] <- "Vocabulary"
# names(d2)[names(d2)=="gort_ori_ss_2"] <- "ORI"
# names(d2)[names(d2)=="ctopp_blending_ss_2"] <- "Blending"
# names(d2)[names(d2)=="ctopp_elision_ss_2"] <- "Elision"
# names(d2)[names(d2)=="ctopp_nonword_ss_2"] <- "Nonword"
# names(d2)[names(d2)=="ran_2set_ss_2"] <- "RAN_2Set"
# names(d2)[names(d2)=="ran_objects_ss_2"] <- "RAN_Objects"
# names(d2)[names(d2)=="wais_dsb_ss_2"] <- "DigitsBackward"
# names(d2)[names(d2)=="wais_dsf_ss_2"] <- "DigitsForward"
# names(d2)[names(d2)=="kbit_ss_2"] <- "IQ"
# names(d2)[names(d2)=="abcd_id"] <- "PartID"
# 
# x<-d2%>%ungroup%>%dplyr::select(PartID,Age,Sex,IQ,SWE,WID,WA,SWE,PDE,
#                                        Vocabulary,ORI,Elision,ORI,Nonword,RAN_2Set,DigitsForward,DigitsBackward)
# x<-na.omit(x)
# 
# d_demo<-merge(demo,x,"PartID")
# d_demo<-merge(d_demo,groups,"PartID")
# 
# table(d_demo$Subgroup)
# table(d_demo$read_delay,d_demo$Subgroup)
# table(d_demo$lang_delay,d_demo$Subgroup)
# table(d_demo$ADHD,d_demo$Subgroup)
# demo_table<-d_demo%>%select(Subgroup,read_delay,lang_delay,dyslexia,ADHD,self_ed,starts_with('race'),household_income,Sex)
# 
# demo_table$self_ed <- factor(demo_table$self_ed,
#                                 levels = c(1,2,3,4,5,6,7),
#                                 labels = c("Less7Grd", "JuniorHigh", "HighSchool","PartialCollege","College","Masters","Doctorate"))
# demo_table$household_income <- factor(demo_table$household_income,
#                                 levels = c(1,2,3,4),
#                                 labels = c("<30k", "30-60k", "60-100k",">100k"))
# 
# cat.names = demo_table %>% select_if(is.integer) %>% colnames()
# demo_table2=demo_table
# demo_table2[,cat.names] = lapply(demo_table2[,cat.names], as.factor)
# str(demo_table2[,cat.names])
# 
# at<-summary(tableby(Subgroup ~ ., data = demo_table2,
#                      control=tableby.control(numeric.stats="meansd", total=FALSE)),title = "Adult Descriptives",text=TRUE,digits=2, digits.p=3)
# at
```
